Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-04-26 LICS2021-final-with-appendices-for-arxiv.tex
put colouring definition back to standard one (no adjacent vertices of same colour), since that's actually shorter than the footnote about not doing it

A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
has a \bfit{label} $\labelof v\in L$ associated with it.
A graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
equivalence relation $\linkingof\gG$ on $\vG$; each equivalence class
is a \bfit{colour}.\footnote{In \cite{hughes:fopws}
adjacent vertices are required to have distinct colours, since it
is part of the standard definition of colouring in graph
theory.
However, this condition is redundant (ommitted here), since it is implied
by the preclusion of bimatchings in the next section.}
%Therefore we do not have this additional condition here.}
A \bfit{vertex renaming} of
$\gG=\tuple{\vG,\eG}$ along a bijection
$(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
theory, we identify graphs modulo vertex renaming.

>>>>

A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
has an associated \bfit{label} $\labelof v\in L$.
A graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
equivalence relation $\linkingof\gG$ on $\vG$
such that $v\linkingof\gG$ only if $vw\tightnotin\eG$; each equivalence class
is a \bfit{colour}.
% \footnote{In \cite{hughes:pws} and \cite{hughes:fopws}
% adjacent vertices must have distinct colours, as
% is part of the standard definition of colouring in graph
% theory.
% We choose to omit this condition, since it is implied
% by the preclusion of bimatchings in Def.\,\ref{def:fonet}.}
% %Therefore we do not have this additional condition here.}
A \bfit{vertex renaming} of
$\gG=\tuple{\vG,\eG}$ along a bijection
$(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
theory, we identify graphs modulo vertex renaming.
